Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
More detailed photos of AVIS

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.

>>>>

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
Six geophones measure the payload velocity and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform.
Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
%TODO: include benchmark section about vibration isolation
